\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{geometry}
\usepackage{color}
\usepackage{verbatimbox}
\geometry{margin=2cm}

\usepackage{url}
\usepackage{tcolorbox}
\usepackage{multirow}
\usepackage{float}

\usepackage{setspace}
\onehalfspacing

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\newcommand\tab[1][1cm]{\hspace*{#1}}

\title{Running All-Si tracker simulations with Fun4All on Cori}
\author{Reynier Cruz Torres \\ (borrowing some text from D. Dixit and F. Torales-Acosta)}

\begin{document}

\maketitle

\tableofcontents

% ========================================================================================
\newpage
\section{Logging into Cori and getting Fun4All working}

First, ssh into cori (\verb|ssh -Y username@cori.nersc.gov|) and go to the directory where Fun4All is to be installed.
Clone the Singularity container from Github and install the package following:

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
git clone https://github.com/sPHENIX-Collaboration/Singularity.git
cd Singularity/
./updatebuild.sh
shifter --image=docker:ddixit/fun4all:eicresearch /bin/bash
\end{verbnobox}  
\end{tcolorbox}

The last command line above lets you enter the docker image using shifter and sets the shell to bash.

Note: here we write short paths for simplicity, but full paths should be used.
For example, the \verb|sphenix_setup.sh| script is located inside:

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
Singularity/cvfms/sphenix.sdcc.bnl.gov/x8664_sl7/opt/sphenix/core/bin/sphenix_setup.sh
\end{verbnobox}  
\end{tcolorbox}

but here we will write it as \verb|local_path_to/opt/sphenix/core/bin/sphenix_setup.sh| because it is likely that the \verb|x8664_sl7| number might be different for different users.
Thus, it is important to remember where your Singularity folder is located, and map out your paths correctly.

\subsection{Modifying the setup script (only need to follow these steps once)}
The following steps are to modify and run the setup script in order to give your access to root as well all the sPHENIX libraries, object, and header files.
In the code below, change \verb|new.#| with the actual number you see associated with the new. directory in your path. For example, if it says \verb|release/release_new/new.2|, use \verb|new.2|

\begin{enumerate}
\item Open \verb|local_path_to/opt/sphenix/core/bin/sphenix_setup.sh| using a text editor.
\item Find the line \verb|if [ -z "$OFFLINE_MAIN" ]|
\item Modify that if statement block (in bash if statements start with ``if'' and end with ``fi'') to look like this:

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
if [ -z "$OFFLINE_MAIN" ]
then
  if [ ! -d ${optbasepath}/release/release_new/$opt_v ]
  then
    opt_v="new.#"
  fi
  export OFFLINE_MAIN=${optbasepath}/release/release_new/$opt_v
fi
\end{verbnobox}  
\end{tcolorbox}

where you change \verb|new.#| with the actual number you see associated with the ``new'' directory in your path. For example, if it says \verb|release/release_new/new.2|, use \verb|new.2|.
This should make \verb|$OFFLINE_MAIN| point to where all your sPHENIX code is located.
For example, a path could look like:

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
Singularity/cvmfs/sphenix.sdcc.bnl.gov/x8664_sl7/release/release_new/new.2/
\end{verbnobox}  
\end{tcolorbox}

and in this directory, you should have the following (you can check this with an ls):
bin  geant4  include  lib  rebuild.info  rebuild.log  root  sartre  share

\item Save \verb|sphenix_setup.sh|.

\item In the terminal, run: \verb|source local_path_to/opt/sphenix/core/bin/sphenix_setup.sh -n|

\item Check that the setup was successful by running in the terminal: \verb|lsb_release -a|.
You should see the following output:

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
LSB Version:	:core-4.1-amd64:core-4.1-ia32:core-4.1-noarch
Distributor ID:	Scientific
Description:	Scientific Linux release 7.3 (Nitrogen)
Release:	7.3
Codename:	Nitrogen
Input: root #see if root works for you.
\end{verbnobox}  
\end{tcolorbox}

\end{enumerate}

At this stage you can also run \verb|root| in the terminal to check that Root is already working.
Once you have root working, try the steps from the ``Try an event display'' tutorial here:

\href{https://github.com/sPHENIX-Collaboration/macros}{https://github.com/sPHENIX-Collaboration/macros}

Remember, we will be using \verb|sphenix_setup.sh| not \verb|.csh|. If the you can run ``Try an event display successfully'', congratulations, you are able to run Fun4All on Cori.
Finally, create a directory called \verb|install| inside the Singularity directory.

\subsection{Using Fun4All from now on (follow these steps every time you log into Cori)}
\label{sec:every_login}

From now on, you will always have to do the following steps to access Fun4All again on Cori:

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
shifter --image=docker:ddixit/fun4all:eicresearch /bin/bash
source local_path_to/opt/sphenix/core/bin/sphenix_setup.sh -n
export MYINSTALL=/global/path/to/Singularity/install
source Singularity/cvmfs/sphenix.sdcc.bnl.gov/x8664_sl7/opt/sphenix/core/bin/setup_local.sh $MYINSTALL
\end{verbnobox}  
\end{tcolorbox}

Step 1 enters the Singularity image, and Step 2 sets up all environment variables.

% ========================================================================================
\newpage
\section{Additional repositories}

\subsection{Building a package}
\label{sec:build}

The steps are explained in detail in the following page in the ``Building a package'' section:

\href{https://wiki.bnl.gov/sPHENIX/index.php/Example_of_using_DST_nodes}{https://wiki.bnl.gov/sPHENIX/index.php/Example\_of\_using\_DST\_nodes}

The basic steps are the following:

\begin{enumerate}
\item Create a build directory. For instance, if the package that will be installed is called ``package'', do \verb|mkdir build_package|.
\item Go into this directory: \verb|cd build_package|.
\item \verb|path/to/package/source/autogen.sh --prefix=$MYINSTALL|.
\item \verb|make install -j 4|
\item Lastly, redo the last three steps from section~\ref{sec:every_login}:

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
source local_path_to/opt/sphenix/core/bin/sphenix_setup.sh -n
export MYINSTALL=/global/path/to/Singularity/install
source Singularity/cvmfs/sphenix.sdcc.bnl.gov/x8664_sl7/opt/sphenix/core/bin/setup_local.sh $MYINSTALL
\end{verbnobox}  
\end{tcolorbox}

\end{enumerate}

\subsection{Jet Analysis}

From inside the Singularity directory, clone the repository \href{https://github.com/ftoralesacosta/e_Jet_sPHENIX}{here}:

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
git clone https://github.com/ftoralesacosta/e_Jet_sPHENIX
\end{verbnobox}  
\end{tcolorbox}

Follow the steps from section~\ref{sec:build} to build this package.

\subsection{All-Silicon tracker}

The All-Silicon Tracker we have been studying at LBNL can be found \href{https://github.com/eic/g4lblvtx}{here}.
From inside the Singularity directory, clone the repository:

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
git clone https://github.com/eic/g4lblvtx
\end{verbnobox}  
\end{tcolorbox}

Follow the steps from section~\ref{sec:build} to build this package.

% ========================================================================================
\newpage
\section{Running All-Si tracker code}

\subsection{Code details}

The main macro is: \verb|g4lblvtx/macros/Fun4All_G4_FastMom.C|.
This section describes some details from this code.

\subsubsection{Detector geometry}

The detector geometry was created in EICroot, saved into a TGeo file, and then translated into a gdml file. The gdml
file where the detector geometry is defined is: \verb|FAIRGeom.gdml|, and is loaded in the main macro in the lines that read:

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
AllSiliconTrackerSubsystem *allsili = new AllSiliconTrackerSubsystem();
allsili->set_string_param("GDMPath","FAIRGeom.gdml");

allsili->AddAssemblyVolume("VST");      // Barrel
allsili->AddAssemblyVolume("FST");      // Forward disks
allsili->AddAssemblyVolume("BST");      // Backward disks
allsili->AddAssemblyVolume("BEAMPIPE"); // Beampipe
\end{verbnobox}
\end{tcolorbox}
	
\subsubsection{Event generator}

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
const int particle_gen = 1;
\end{verbnobox}
\end{tcolorbox}

Below are the possible settings for this variable:

\begin{itemize}
\item \verb|particle_gen = 1|, the generator used is a particle generator, which generates a given particle per event over an extended range in angles, momenta, etcetera.
\item \verb|particle_gen = 2|, the generator used is a particle gun, which shoots the same particle with the same properties (angles, momenta, ...) over and over. 
\item \verb|particle_gen = 3|, the generator used is a ``simple event generator'' (using the Fun4All class \verb|PHG4SimpleEventGenerator|) which can generate, for example, 100-pion events.
This cab be used for primary-vertex studies.
\item \verb|particle_gen = 4|, the generator used is pythia8.
\end{itemize}

\subsubsection{Magnetic field}

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
const int magnetic_field = 4;   // 1 = uniform 1.5T, 2 = uniform 3.0T, 3 = sPHENIX 1.4T map, 4 = Beast 3.0T map
\end{verbnobox}
\end{tcolorbox}

Below are the possible settings for this variable:

\begin{itemize}
\item \verb|magnetic_field = 1|, uniform 1.5 T solenoidal field.
\item \verb|magnetic_field = 2|, uniform 3.0 solenoidal field.
\item \verb|magnetic_field = 3|, realistic sPHENIX (BaBar) 1.4 T magnetic-field map.
\item \verb|magnetic_field = 4|, realistic Beast 3.0 T magnetic-field map.
\end{itemize}

% ========================================================================================

\subsection{Running All-Si code on login node}

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
root -l Fun4All_G4_FastMom.C
\end{verbnobox}
\end{tcolorbox}

or by first loading root, and then doing:

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
.x Fun4All_G4_FastMom.C
\end{verbnobox}
\end{tcolorbox}

\subsection{Running batch jobs on Cori}

Some tips to get started with Slurm can be found \href{https://slurm.schedmd.com/quickstart.html}{here}.

\href{https://github.com/eic/g4lblvtx/tree/master/cori_batch}{Here} is an example on how to submit a batch job on Cori.
To submit the jobs from \verb|run_shared_pim.sh| do the following:

\begin{enumerate}
\item exit the container: \verb|exit|
\item go to the directory where \verb|run_shared_pim.sh| is.
\item run: \verb|sbatch run_shared_pim.sh|
\end{enumerate}

To check the status of your jobs, go in your internet browser to \href{https://my.nersc.gov/}{https://my.nersc.gov/} and login.
Then go to the tab ``Cori Queues''.
Alternatively, you can run in the terminal (from outside the Singularity container):

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
squeue -u username
\end{verbnobox}  
\end{tcolorbox}

To cancel all submitted jobs, you can run in the terminal (from outside the Singularity container):

\begin{tcolorbox}
\begin{verbnobox}[\scriptsize]
scancel -u username
\end{verbnobox}  
\end{tcolorbox}

%\bibliography{bib_file}
%\bibliographystyle{ieeetr}

\end{document}





